JMS

### 2021-01-23 analysis.Rmd
remove JMS

library(knitr)
library(ggplot2)
library(forcats)
library(reshape2)
library(tidyr)
library(dplyr)
library(reshape)
library(gtable)
library(explore)
library(gridExtra)
library(xtable)
library(ggpubr)

#  This was to simplify dataset of basic conditions
# a <- read.csv("basic_equal.csv", sep = ",", skip = 6)
# names(a) <- pull(read.csv("legend.csv"))
# B <- a %>% filter(dominant >= 0, secondary_circle  <= dominant, secondary_square <= dominant) %>% filter(ticks == 1000)
# write.csv(B, file = "basic_exp.csv", row.names = FALSE)

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/experiments/JMS/")

hc_hc_dis <- read.csv("hc_hc_dis.csv")
# names(test_mj80) <- pull(read.csv("legend_test.csv"))

base_eq <-  read.csv("basic/basic_exp.csv", sep = ",")

majority_bs <- read.csv("maj/majority_bs.csv", sep = ",", skip = 6)
names(majority_bs) <- pull(read.csv("basic/legend_bas.csv"))

majority_bsa <- read.csv("maj/majority_bsa.csv", sep = ",", skip = 6)
names(majority_bsa) <- pull(read.csv("basic/legend_bas.csv"))
names(majority_bsa)[names(majority_bsa) == "circle_orange"] <- "dmnt"
names(majority_bsa)[names(majority_bsa) == "dominant"] <- "circle_orange"
names(majority_bsa)[names(majority_bsa) == "dmnt"] <- "dominant"

majority_bs <- majority_bs %>% filter(ticks == 1000)

# majlib <- read.csv("maj/maj_lib.csv", sep = ",", skip = 6)
# names(majlib) <- pull(read.csv("maj/legend_maj.csv"))

test_5_20 <- read.csv("result5_20.csv", sep = ",", skip = 6)
names(test_5_20) <- pull(read.csv("legend_test.csv"))
test_5_20 <- test_5_20[,-(35:42)]

test_20_5 <- read.csv("result20_5.csv", sep = ",", skip = 6)
names(test_20_5) <- pull(read.csv("legend_test.csv"))

b <- test_20_5 %>% filter(fraction_blue == 60)

a <- test_5_20 %>% filter(fraction_blue == 80)
ftable(xtabs(~ a$circle_orange + a$eth_loc_lib + a$eth_min_lib, data = a))

levels(as.factor(a$eth_loc_con))
levels(as.factor(b$eth_loc_con))

>>>>

library(knitr)
library(ggplot2)
library(reshape)
library(reshape2)
library(forcats)
library(tidyr)
library(dplyr)
library(gtable)
library(kableExtra)
library(magick)
library(webshot)
library(xtable)
library(gridExtra)
library(ggrepel)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
webshot::install_phantomjs()

setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")

# Back work, used to combine datasets from diffent runs. To IGNORE OR DELETE

# etlib_min1 <- read.csv("mj_etlib_min.csv",skip = 6)
# etlib_min2 <- read.csv("mj_etlib_min2.csv",skip = 6)
# etlib_min <- rbind(etlib_min1,etlib_min2)
# names(etlib_min) <- pull(read.csv("legend_sec_etlib.csv"))
# etlib_min <- cbind(ID = "etlib_min",etlib_min)

basic <- read.csv("df_basic.csv",sep =",")
value_basic <- read.csv("df_valuebasic.csv",sep = ",")
asym_dom <- read.csv("df_asym_dom.csv",sep = ",")
dislib <- read.csv("df_dislib.csv", sep = ",")
sa_asym <- read.csv("df_sa_asym.csv",sep =",")
etlib <- read.csv("df_etlib.csv",sep =",")

circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
names(circle_orange.labs) <- c("20","50","80")
```

```{r basefigure, fig.width=30, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}

# database filter
excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

# graph

data_f <- basic_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
  xlab("ß dominant = ß secondary") + ylab("Exposure") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("images/one_beta.jpg",plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 10,
  height = 4,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

# robustness table

table_rb <- xtable(basic_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline condition}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ dom = $\\beta$ sec & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

print(table_rb,type = "latex", file = "basic_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

```{r secondary_0, fig.width=30, fig.cap="secondary preference set to 0", echo=FALSE}

# database filter
excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa_sec0 <- basic[!excl] %>% filter(secondary == 0) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))

# graph

data_f <- basic_sa_sec0 %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
  xlab("ß dominant") + ylab("Exposure") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("images/sec_0.jpg",plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 10,
  height = 4,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

# robustness table

table_rb <- xtable(basic_sa_sec0[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Secondary preference = 0}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

print(table_rb,type = "latex", file = "basic_rb_sec0.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

```{r base_lib, fig.width=30, fig.cap="Test mechanism: increase value liberal, all other 0", echo=FALSE}

# database filter
excl <- names(value_basic) %in% c("run","density","step")
dom_lib <- value_basic[!excl] %>% filter(ID == "dom_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0) %>% 
  group_by(ID, dominant_circle,secondary_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))

# graph

data_f <- dom_lib %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

 dom_libpic <- ggplot(data = data_f, aes(x = dominant_circle, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
  xlab("ß value liberal") + ylab("Exposure") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("images/dom_lib.jpg",plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 10,
  height = 4,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

# robustness table

table_rb <- xtable(dom_lib[,c("dominant_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to value liberal}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
# note
"$\\beta$ dom liberal & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

print(table_rb,type = "latex", file = "dom_lib_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

```{r base_con, fig.width=30, fig.cap="Test mechanism: increase ethnic conservative, all other 0", echo=FALSE}

# database filter
excl <- names(value_basic) %in% c("run","density","step")
dom_con <- value_basic[!excl] %>% filter(ID == "dom_sqr") %>%
   group_by(ID,dominant_square, secondary_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>%
  #secondary_square == 0 & dominant_circle == 0 & secondary_circle == 0) %>% group_by(dominant_square) 
summarise_all(c("mean"= mean,"sd"= sd))

# graph

data_f <- dom_con %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

dom_conpic <- ggplot(data = data_f, aes(x = dominant_square, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
  xlab("ß ethnic conservative") + ylab("Exposure") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("images/dom_con.jpg",plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 10,
  height = 4,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

# robustness table

table_rb <- xtable(dom_con[,c("dominant_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to ethnic conservative}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
# note
"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

print(table_rb,type = "latex", file = "dom_con_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

```{r comb_value, fig.cap="Combined picture, value sensitivity", echo=FALSE}

ggpubr::ggarrange(dom_libpic,dom_conpic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")

ggsave("images/comb_val.jpg",plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 8,
  height = 6,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)
```

```{r asym, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}

# database filter
excl <- names(asym_dom) %in% c("run", "ID","density","step")
dataset_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))

xlab_t <- "ß dominant"

row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

tablerb_expname <- "latex/asym_rb_exp.tex"
tablerb_proxname <- "latex/asym_rb_prox.tex"

plotname <- "images/comb_index.jpg"

# graph

data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

fig_exp <- ggplot(data = data_exp, aes(x = dominant, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  xlab("") + ylab("Exposure") + 
  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  row_exp

print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

## Spatial proximity baseline asymmetric

# graph

data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))

fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  xlab(xlab_t) + ylab("Spatial Proximity") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# robustness table

tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"

addtorow <- list()
addtorow$pos <- list(0, 0,0,0,0)
addtorow$command <-  row_prox
print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")

# combined image

ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 8,
  height = 6,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

```{r dislib, fig.width=30, fig.cap="Effect distribution liberal minority, asymmetric based condition", echo=FALSE}
